Doublet splitting and linear amplitude characteristics of fusion alpha-particle driven ion cyclotron emission

### 2022-01-31 manuscript.tex
tiny word change in caption

\begin{figure}[ht!]
    % \centering
    \raggedleft
\includegraphics[scale=0.9]{fig3.pdf}
    \caption{(colour online) The imaginary component of the frequencies for the case with parallel drift, $u_{\parallel} = -0.64 u_0 \simeq -1.085 V_A$. Panel (a) plots the growth rate against frequency where shading indicates the wave's parallel wavenumber in units of $\Omega_i/V_A$, and (b) plots the solutions in the $k_\parallel, \omega$ plane where shading indicates growth rate. Note that the Doppler shift associated with the non-zero parallel drift speed broadens the unstable peaks in frequency. The 10th cyclotron harmonic is split into a doublet, or has two peaks because both the growth rate and real frequency vary with wavenumber. Compare with Fig. 2 of Cottrel et al 1993.}
    \label{fig:2D_F12_physicalpitch}
\end{figure}

>>>>

\begin{figure}[ht!]
    % \centering
    \raggedleft
\includegraphics[scale=0.9]{fig3.pdf}
    \caption{(colour online) The imaginary component of the frequencies for the case with parallel drift, $u_{\parallel} = -0.64 u_0 \simeq -1.085 V_A$. Panel (a) plots growth rate against frequency where shading indicates parallel wavenumber in units of $\Omega_i/V_A$, and (b) plots the solutions in the $k_\parallel, \omega$ plane where shading indicates growth rate. Note that the Doppler shift associated with the non-zero parallel drift speed broadens the unstable peaks in frequency. The 10th cyclotron harmonic is split into a doublet, or has two peaks because both the growth rate and real frequency vary with wavenumber. Compare with Fig. 2 of Cottrel et al 1993.}
    \label{fig:2D_F12_physicalpitch}
\end{figure}
